---
title: "Evaluation of DTSA-II &Phi;(&rho;z)"
author: "J. R. Minter"
date: "Started: 2018-01-23. Last modified: 2018-01-23"
output:
  html_document:
    csl: ./inc/american-chemical-society-with-titles-sentence-case-doi.csl
    css: ./inc/jm-gray-vignette.css
    toc: true
    number_sections: yes
bibliography: ./inc/dt2Conv.bib
---


# Introduction

I need to verify the performance of the DTSA-II PhiRhoZ results output by
the functions in the **mcSimulate3** library. To do this I simulated ZnO2.

# Analysis

## Step 1: Load R packages and the data.

First, let's load the packages we need.

```{r, message=FALSE}
library(ggplot2)
library(latex2exp)
library(rEDS)
library(pander)

bVerbose=TRUE
```

Now let's create a dataframe from the MC3 Phi-Rho-Z **.tsv** file


```{r, readMc315kV,message=FALSE}
id <- '../data/csv/'
fi <- 'ZnO-15.0-keV-MC3-20000-traj-prz.tsv'
df <- prepDataframeDtsaMcPhiRhoZ(id, fi)
```


## Step 2: Make a dataframe with the transitions we care about.

While we are at it, let's change the dataframe headers to make
it easier to make the plots... We are plotting the generated
and emitted X-rays. Let's make simple mnemonics...


```{r makeMC3DF}

z <- df$Z.um
znkgen <- df$Gen.Zn.K.L3.
znkemi <- df$Emit.Zn.K.L3.
znlgen <- df$Gen.Zn.L3.M5.
znlemi <- df$Emit.Zn.L3.M5.

if(bVerbose) print(head(znkgen))
if(bVerbose)print(head(znkemi))

dfMC3 <- data.frame(Z.um=z,
                  Zn.K.Gen=znkgen,
                  Zn.K.Emi=znkemi,
                  Zn.L.Gen=znlgen,
                  Zn.L.Emi=znlemi)

pander(head(dfMC3))
```

Note that my initial assumption was that the distance values were in microns.


## Step 3 - Make a DTSA PAP1991 phi-rho-z dataframe

```{r, readPAP15kV,message=FALSE}
fi <- '../data/csv/ZnO-prz-Z-15-kV.csv'
df <- read.csv(fi, header=TRUE)

z <- df$Z.um
znkgen <- df$G.Zn.K.L3.
znkemi <- df$E.Zn.K.L3.
znlgen <- df$G.Zn.L3.M5.
znlemi <- df$E.Zn.L3.M5.

df <- data.frame(Z.um=z,
                        Zn.K.Gen=znkgen,
                        Zn.K.Emi=znkemi,
                        Zn.L.Gen=znlgen,
                        Zn.L.Emi=znlemi)
dfPAP1991  <- df[-1,] # get rid of zero row
rownames(dfPAP1991) <- c()
pander(head(dfPAP1991))
```


## Step 4: Measure the maximum values of the emitted data

```{r, maxVals}
znKMC3 <- max(dfMC3$Zn.K.Emi)
znKPAP1991 <- max(dfPAP1991$Zn.K.Emi)
znLMC3 <- max(dfMC3$Zn.L.Emi)
znLPAP1991 <- max(dfPAP1991$Zn.L.Emi)

ID <- c("Zn-K MC3", "Zn-K PAP", "Zn-L MC3", "Zn-L PAP")
maxPRZ <- c(znKMC3, znKPAP1991, znLMC3, znLPAP1991)

dfMax <- data.frame(ID=ID, maxPRZ=maxPRZ)

pander(dfMax)
```

Note that the Zn-L MC3 maximum is much too large.

## Step 5: Plot the Zn K data

```{r, pltZnK}

szP <- 2
szL <- 4

plt <- ggplot() +
       geom_point(data=dfPAP1991, aes(x=Z.um, y=Zn.K.Emi),
                  size = szP, colour="darkblue") +
       annotate("text", label = 'PAP1991 Zn K-L3 emitted',
                       x = 0.75, y = 1.25,
                       size = szL, colour = "darkblue") +
       
       geom_point(data=dfMC3, aes(x=Z.um, y=Zn.K.Emi),
                  size = szP, colour="darkred") +
       annotate("text", label = 'MC3 Zn K-L3 emitted',
                       x = 0.75, y = 1.15,
                       size = szL, colour = "darkred") +
       ylab(label="Zn K-L3 \U03D5(\U03C1z)") +
       xlab("depth [\U00B5m]") +
       ggtitle("DTSA-II measures or of Zn-K \U03D5(\U03C1z) at 15 kV") +
       theme(axis.text=element_text(size=12),
             axis.title=element_text(size=14),
             plot.title = element_text(hjust = 0.5))
  

print(plt)
```

Something is still not right...

# References





